### 2023-09-07 Paper/main.tex
Fix typos

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\usepackage{listings}
\begin{document}

@@

To encode the loss less images into the respective codec for the experiment, several encoder where used. 
\subsection{AVIF, JPEG and WebP}
For those encoders the python package pillow-avif-plugin and pillow was used. The additional pillow plugin can be installed via pip install pillow-avif-plugin. To encode a lossless image, the image is opened and save with a specific quality as seen in \ref{avif_1}. The quality parameter ranges from 1(lowest) to 100(highest). It is important to set the specific file extension for the software to 
know in which codec the image needs to be encoded.
\begin{lstlisting}[label={avif_1}, language=Python, caption=Encode AVIF\, JPEG and WebP]
image = Image.open(image_path)
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{BPG}
To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used. As seen in \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument. The quality parameter ranges from 51(lowest) to 0(highest). The last argument that needs no specific indicator is the original image.

@@

\subsection{HEIC}
Same as with the AVIF codec HEIC is also supported in a python package. For this codec the package pillow\_heif which can be installed with pip pillow-heif. The quality parameter ranges from 1(lowest) to 100(highest).
How the image can be encoded in HEIC is shown in \ref{heic_1}.

@@

\subsection{JPEG2000}
For the JPEG standards JPEG itself provides software to encode images. In the experiment the libopenjp2 was used. This library is in the Linux package manager and can be installed with apt-get install libopenjp2-tools. The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter. An example how this can be done in Python is shown in \ref{jpeg2k_1}.
\begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
subprocess.call('opj_compress -o ' + outputPath + \
                ' -r ' + str(int(maxQ - q)) + \
                ' -i ' + image_path,
                stdout=subprocess.DEVNULL,
                stderr=subprocess.DEVNULL,
                shell=True)
\end{lstlisting}

@@

\section{RESNET explanation (Stef)}

@@

The idea behind training the network from scratch is that the network would be mor tailored to the given task since it has no previous information stored in the network. This contrasts with transfer learning since there prior information is present.
\newline

@@

\noindent
To train the network the DIV2K training and validation Dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. This leads to 10 classes – one for each compression algorithm – for each file size category. We trained the network by using the images that were compressed to a file size of 25kB.
\newline

@@

\subsection{Transferlearning}
For this approach the ResNet18 model was used as a baseline. To adjust this pre trained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.

@@

\noindent
The smaller filesize models have their peaks arround the filesizes they were trained on. However, for the images with less than 40kB this models have an accuracy of about 95 percent. For the bigger filesizes the accuracy is decreasing. The bigger filesizes have less artifacts in the images and also many codecs get the maximum quality after 60kB, which explains the decrease of accuracy for this models.

>>>>

\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}
\hypersetup{
    colorlinks=true, % Set this to true to remove the border
    linkcolor=black, % Color for internal links
    citecolor=black, % Color for citations
    }
\usepackage{listings}
\usepackage{blindtext}
\usepackage{geometry}
\geometry{margin=25mm}
\begin{document}

@@

To encode the loss less images into the respective codec for the experiment, several encoder where used.
\subsection{AVIF, JPEG and WebP}
For those encoders the python package pillow-avif-plugin and pillow was used. The additional pillow plugin can be installed via pip install pillow-avif-plugin. To encode a lossless image, the image is opened and save with a specific quality as seen in listing \ref{avif_1}. The quality parameter ranges from 1(lowest) to 100(highest). It is important to set the specific file extension for the software to
know in which codec the image needs to be encoded.
\begin{lstlisting}[label={avif_1}, language=Python, caption=Encode AVIF\, JPEG and WebP]
image = Image.open(image_path)
image.save(outputPath, quality=q)
\end{lstlisting}

\subsection{BPG}
To encode the images in BPG the Linux distribution from Fabrice Bellard's website (https://bellard.org/bpg/) was used. As seen in listing \ref{bpg_1} the output path is given after the -o argument and the specific quality after the -q argument. The quality parameter ranges from 51(lowest) to 0(highest). The last argument that needs no specific indicator is the original image.

@@

\subsection{HEIC}
Same as with the AVIF codec HEIC is also supported in a python package. For this codec the package pillow\_heif which can be installed with pip pillow-heif. The quality parameter ranges from 1(lowest) to 100(highest).
How the image can be encoded in HEIC is shown in listing \ref{heic_1}.

@@

\subsection{JPEG2000}
For the JPEG standards JPEG itself provides software to encode images. In the experiment the libopenjp2 was used. This library is in the Linux package manager and can be installed with apt-get install libopenjp2-tools. The quality parameter which ranges from 1(lowest) to 1000(highest) is given to the software with the -r parameter. An example how this can be done in Python is shown in listing \ref{jpeg2k_1}.
\begin{lstlisting}[label={jpeg2k_1}, language=Python, caption=Encode JPEG 2000]
subprocess.call('opj_compress -o ' + outputPath + \
                ' -r ' + str(int(maxQ - q)) + \
                ' -i ' + image_path,
                stdout=subprocess.DEVNULL,
                stderr=subprocess.DEVNULL,
                shell=True)
\end{lstlisting}

@@

\section{RESNET explanation}

@@

The idea behind training the network from scratch is that the network would be more tailored to the given task since it has no previous information stored in the network. This contrasts with transfer learning since there prior information is present.
\newline

@@

\noindent
To train the network the DIV2K training and validation dataset was used. The dataset contains 800 train images and 100 test images. Since the images had different dimensions, we first had to crop them to specific in this case 512x512. Afterwards we compressed the images to specified file sizes as described in \ref{sec: filesize}. This leads to 10 classes – one for each compression algorithm – for each file size category. We trained the network by using the images that were compressed to a file size of 25kB.
\newline

@@

\subsection{Transferlearning}
For this approach the ResNet18 model was used as a baseline. To adjust this pretrained model for the requirements of the experiment, the output layers where reconfigured to represent the 8 different codecs in which the images where encoded.
In addition the model uses just 224x224 images as inputs, thus the encoded images where center cropped to fit that size.

@@

\noindent
The smaller filesize models have their peaks around the filesizes they were trained on. However, for the images with less than 40kB this models have an accuracy of about 95 percent. For the bigger filesizes the accuracy is decreasing. The bigger filesizes have less artifacts in the images and also many codecs get the maximum quality after 60kB, which explains the decrease of accuracy for this models.
